|

### 2022-12-13 paper_comparison/paper_comparison/paper_comparison.Rmd
clarify non-normality is not the focus in the experiment design

# Experimental design

(This section discusses the experimental design including the motivation of the experiment, an overview of the experiment, the simulation setting of the depatures from good residual plots, parameter choices, allocation of the lineups and other technical details.)

<!-- ## Experiment overview-->

<!-- With our knowledge, the effectiveness of visual test relative to the equivalent conventional test in regression diagnostics has not been validated. Particularly, its ability to detect non-linearity and heteroskedasticity compared to model structural test and Breusch–Pagan test. Meanwhile, as mentioned in Section \ref{introduction} section, we keen to understand the differences between conventional hypothesis testing and graphical diagnostics in the application of linear regression diagnostics and why conventional tests are not preferred by data analysts in linear regression diagnostics. Attempting to find the answer to these questions, three experiments were conducted. -->

@@

Two types of departures, namely non-linearity and heteroskedasticity, were considered with the corresponding data generating process being designed for experiment I and II.

>>>>

# Experiment design

@@

Two types of departures, namely non-linearity and heteroskedasticity, were considered with the corresponding data generating process being designed for experiment I and II. As mentioned earlier, residual plot is not suitable for revealing non-normality, thus it was not considered in our experiments.
